### 2018-10-03 paper/paper.tex
update paper; LTS cycle; LTS name; started over time part

\documentclass[dvips,mnsc]{informs3}
% [citeauthoryear]

@@

% --------------------

% \usepackage[table]{xcolor}
% \usepackage{xcolor}
% \usepackage[utf8x]{inputenc}
% \usepackage{listings}
% \usepackage{amsmath,amssymb}
% \usepackage[noend]{algpseudocode}
% \usepackage{stmaryrd}
% \usepackage{listings}
% \usepackage{algorithm}
% \usepackage{array}
% \usepackage{textcomp}
% \usepackage{pifont}
% \usepackage{bbding}
% \usepackage{comment}
% \usepackage{graphicx}
\usepackage{paper}
% \usepackage[svgpath=figures/]{svg}
% \usepackage[labelfont=bf]{caption}
% \captionsetup[table]{skip=5pt}

@@

Lead Time Syndrome (LTS)

@@

In this section we present a formalisation of the \LTS{}. It is straightforward to implement the
presented methods to establish a \LTS{} detection system. We follow the notation established
by~\cite{selccuk2013adaptive}.

@@

Consider a single product one-stage manufacturing system that releases orders from the order pool
into the production system by an external mechanism. We denote the demand rate at time
$t \geqslant 0$ as $\dr{t}$, and the demand for the item during the period defined by timestamps
$t_{2} \geqslant t_{1} \geqslant 0$ as $\di{t_{1}}{t_{2}}$. Similarly we denote the order release
rate as $\rr{t}$ and the releases within a period as $\ri{t_{1}}{t_{2}}$. Usually

@@

  The overall queue length

@@

>>>>

\documentclass[mnsc]{informs3}
% [citeauthoryear]

@@

% --------------------
\usepackage[utf8x]{inputenc}
% \usepackage[table]{xcolor}
% \usepackage{xcolor}
% \usepackage{listings}
% \usepackage{amsmath,amssymb}
% \usepackage[noend]{algpseudocode}
% \usepackage{stmaryrd}
% \usepackage{listings}
% \usepackage{algorithm}
% \usepackage{array}
% \usepackage{textcomp}
% \usepackage{pifont}
% \usepackage{bbding}
% \usepackage{comment}
% \usepackage{graphicx}
\usepackage{paper}
% \usepackage[svgpath=figures/]{svg}
% \usepackage[labelfont=bf]{caption}
% \captionsetup[table]{skip=5pt}

@@

Introduce abbreviations:
\begin{itemize}
\item Lead Time Syndrome (\LTS{})
\item Work-in-process (\WIP{})
\end{itemize}

Related literature \MS[t]{Cite!} argues that the lead time syndrome can only occur (i) if a lead
time is set dynamically and nonreciprocal according to the current \WIP{}-level and (ii) the order
releases monotonically depend on this lead time. In a practical point of view this assumption is
correct, however theoretically the interconnection between \WIP{}-level and number of releases is
not needed to infer this systematic releasing misbehavior.

\begin{proof}{Proof}
  Consider a manufacturer with constant demand and an order release mechanism which strictly
  increases the number of orders to be released on every release decision, e.g.~by 1 order. Clearly
  the release decision does neither depend on the flow time nor lead time. However, considered over
  time this leads to a monotonically increasing \WIP{}-level which again leads to a monotonically
  increasing lead time.\qed
\end{proof}

% \MS{name clash: LEAD TIME Syndrome with no LEAD TIME?}
Despite this theoretical observation the name lead time syndrome may be under question. However, as
in cases as given in the proof above the lead time follows the order release decisions and in
practice order releases are usually determined by the lead time (or flow time) the wording can be
considered as appropriate.

@@

In this section we present a formalisation of the \LTS{}.
%
\MS[t]{TODO} The section is split into two
parts. First we will present the method for single-stage manufacturers, before considering more
stages.
%
It is straightforward to implement the presented methods to establish a \LTS{} detection system, see
Section~\ref{sec:Experimental_Evidence}. We follow the notation established
by~\cite{selccuk2013adaptive} to ease readability.

@@

Consider a single product one-stage flow-shop manufacturing system that releases orders from the
order pool into the production system by an external mechanism.
%
Usually the orders are released based on the observed (average) flow time of the last finished
orders. However, our method does not presuppose such an interdependence for detecting the lead time
syndrome as it works directly on (parts of) the \WIP{}-level of the system.
%
% Intuitively the method works as
% follows. By measuring the change of the average \WIP{}-level over time and comparing this to the
% average releases into the system it can infer the desired property.
%
We denote the demand rate at time $t \geqslant 0$ as $\dr{t}$, and the demand for the item during
the period defined by timestamps $t_{2} \geqslant t_{1} \geqslant 0$ as $\di{t_{1}}{t_{2}}$.
Similarly we denote the order release rate as $\rr{t}$ and the releases within a period as
$\ri{t_{1}}{t_{2}}$. Each work-station $i$ is equipped with a queue $\q_{i}$ on which released
orders are appended according to a given routing and from there handed over to the work-station if
only if the work-station is empty and the order is at the head of the queue. Thus we allow parallel
processing of unique orders with non-shared queues in the setup. In case of shared queues in this
single item setup the work-station shall be considered as a single work-station. The size of a queue
$\size{\q_{i}} \geqslant 0$ is given by the number of orders within the queue.

@@

  The queue size $\size{\Q_{i}}$ of stage $i$ is defined as
  $\size{\Q_{i}} = \sum_{i=1}^{n} \size{\q_{i}}$, where $n$ is the number of work-stations of stage
  $i$. Note that in this subsection we set $i=1$.

@@

As the demand may vary over time, e.g.~in a seasonal pattern or simply by some variance, it must be
considered as time factor in formulation of the lead time syndrome. To clarify, consider a seasonal
demand. It can clearly not be considered a lead time syndrome if the releases just depict the
demand. However

and therefore
specifies the
